\documentclass[a4paper,10pt]{article}
\usepackage[left=0.5in,right=0.5in,top=0.7in,bottom=0.7in]{geometry}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}

% Define colors
\definecolor{darkblue}{RGB}{26,13,171}

% Define section formatting
\titleformat{\section}{\Large\bfseries\color{darkblue}}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{1em}{0.5em}

% Define subsection formatting
\titleformat{\subsection}{\color{darkblue}}{}{0em}{}
\titlespacing{\subsection}{0pt}{0.5em}{0.5em}

% Define URL formatting
\makeatletter
\def\url@myformat#1{\color{darkblue}{\texttt{\url{#1}}}}
\makeatother
\urlstyle{myformat}

% Remove section numbering
\setcounter{secnumdepth}{0}

% Adjust font
\renewcommand{\rmdefault}{phv}
\renewcommand{\sfdefault}{phv}

% Set line spacing
\renewcommand{\baselinestretch}{1.2}

\begin{document}

\begin{center}
    \textbf{\Huge Syed Mohsin Bukhari} \\
    \vspace{0.5em}
    \small
    \textit{Embedded and Software Engineer} \\
    \vspace{1em}
    \begin{tabular}{p{10cm}p{6cm}}
        \textbf{Address:} Srinagar, Jammu \& Kashmir, India & \textbf{Phone:} +918491000275 \\
        \textbf{Email:} \url{smayour82@gmail.com} & \textbf{LinkedIn:}\url{www.linkedin.com/in/syed-mohsin-bukhari} \\
    \end{tabular}
\end{center}

\section{OBJECTIVE}
Seeking a challenging position as an Embedded and Software Engineer where I can contribute my skills in electronics and programming to drive innovation and achieve remarkable results.

\section{EXPERIENCE}
\textbf{Amargarh Grid Station} \hfill \textit{Dec 2022 - Feb 2023} \\
Intern

\section{EDUCATION}
\textbf{Islamic University of Science \& Technology, Pulwama} \\
Bachelor of Technology - BTech \hfill \textit{Sep 2019 - Jul 2023} \\
\textbf{Grade:} A

\section{SKILLS}
\begin{minipage}{0.5\textwidth}
    \textbf{Programming:}
    \begin{itemize}[left=0pt]
        \item MATLAB
        \item Python
        \item Embedded C
        \item HTML, CSS, JavaScript
    \end{itemize}
\end{minipage}%
\begin{minipage}{0.5\textwidth}
    \textbf{Technologies:}
    \begin{itemize}[left=0pt]
        \item VHDL
        \item IoT
        \item Computer Vision
        \item Machine Learning, Artificial Intelligence 
    \end{itemize}
\end{minipage}\\

\textbf{Tools:} KiCAD, Arduino, Multisim, Xilinx Vivado, TinkerCAD, Raspberry Pi, LabVIEW

\section{PROJECTS}
\textbf{Personal Portfolio website} \\
\url{https://mayourbukhari.github.io/Personal-Portfolio/} \hfill \textit{Oct 2023} \\
Discover my professional journey on my portfolio website.

\textbf{Fruit Grading \& Sorting System} \hfill \textit{Jan 2022} \\
Automatic grading \& sorting of fruits \& dry fruits.

\textbf{Traffic Control System} \hfill \textit{Aug 2023} \\
Intelligent traffic signal regulation using IR sensors.

\textbf{Visionary Fruit Sort} \\
\url{https://visionaryfruitsort.vercel.app/} \hfill \textit{Jul 2023} \\
Explore the site to experience the seamless integration of design and functionality.

\textbf{Keyless Door Lock System} \hfill \textit{Jul 2022} \\
Arduino-based with keypad \& LCD.

\textbf{Gas Detection System} \hfill \textit{Aug 2022} \\
Detects gas leaks \& shuts off the regulator.

\textbf{Automatic Street Light Control} \hfill \textit{May 2022} \\
Smart bulb control using LDR.
\end{document}
